A Data-Driven Framework for Neural Field Modeling

### 2011-01-03 ltx/first_order_framework/response_to_reviews.tex

\item In the isotropic and translationally invariant case examined here, would a Fourier basis for temporal and spatial structure have been a formally correct alternative?\\

\emph{Gaussians have semi-compact support but Fourier basis functions are global functions. Gaussian can be easily extended to higher dimension (don't know about the Fourier basis functions), any orthonormal basis functions like Fourier basis functions simplify our equations, $\Gamma$ becomes identity matrix, but using Gaussian basis functions equations are in their generic form.}

\item In equation 29, what would a reasonable $v_c$ be for a real neuronal system (mammalian) given the number of neurons and scale of electrodes? I am concerned that it might be much higher than any of us wish to consider. One would perhaps be saved by the filter characteristics of brain (e.g. Phys. Rev. E 73, 051911 (2006)).

\emph{The spatial frequency content is seems to be actually lower than one might first think. We have added 'From the work of (Freeman et al, 2000), the expected bandwidth of the human neocortex is approximately 0.4 cycles/mm which requires a maximal sensor spacing of approximately 1.25 mm to avoid distortions due to aliasing' to the Frequency Analysis section of the paper to clear this up. Note, we expect the spatial bandwidth of the cortex to be governed by the connectivity kernel, since it is equivalent to a spatial low-pass filter acting on the firing rates.  }

@@

\item The two covariance inflation parameters in equation 41 make me cringe. How are we best to adjust these fudge factors?\\

\emph{Values for the two parameters in equation 41 along with the relevant references ,that describe the rationale for parameter choice, have been added to the manuscript.}

@@

\emph{This point is clarified by adding the connectivity kernel componets superimposed by the resulting Mexican Hat basis in Figure 1. of the manuscript.}

 \begin{figure*}[!ht]
 \begin{center}
 \includegraphics{./Graph/pdf/fig1.pdf} 
 \end{center}
 \caption{}
 \label{fig:Figure1}
 \end{figure*}

\item A few comments on how to adapt the smoother for real time implementation would be helpful. I presume that one would perform the smoothing during a training phase. But one would also wish to adapt in real time as observation or control scenarios progressed. A few words of perspective would be invaluable to help others translate the author's wisdom on this method to other applications.
\item Figure 4. Should the axes be indicated as spatial frequency rather than just Hz?\\

\emph{Axes of Figure 4. (and also Figure 5.) are now changed to spatial frequency. The unit of the spatial frequency within the text is changed to cycles/mm.}

### 2011-01-03 ltx/first_order_framework/LaTeX_Manuscript.tex
minor correction in table1
added reference for nu_c

% \newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}}
\newcommand{\dean}[1]{\textcolor{red}{#1}}

\newcommand{\parham}[1]{\textcolor{blue}{#1}}

@@

In practice, it is difficult to estimate the bandwidth of the cortex using traditional electrophysiological measurements, possibly preventing placement of sensors in accordance to equation~\ref{eq:MinimumSensorDistance}. However, we envisage it may be possible to estimate the spatial bandwidth using other modalities with higher spatial resolution such as fMRI, NIRS or other optical imaging techniques (\cite{Issa2000}). Spectral aliasing can be avoided by a proper choice of the spatial sampling distance given the sensors' spectral characteristics. The spatial extent of the sensors results in a spectral low-pass action, thus providing spatial anti-aliasing filtering. Such sensors limit the spatial bandwidth of the observation to a value denoted by $\boldsymbol{\nu}_{cy}$. Aliasing can then be avoided by positioning the sensors according to equation~\ref{eq:MinimumSensorDistance}, replacing $\boldsymbol{\nu}_c$ with $\boldsymbol{\nu}_{cy}$.

@@

The sigma vectors are propagated through the system equations and weighted to form the predicted mean and covariance. The weights are calculated by 
\begin{align}
	\mathbf W_0^{(m)}&=\frac{\lambda}{ n_x+\lambda} \\
	\mathbf W_0^{(c)}&=\frac{\lambda}{ n_x+\lambda}+(1-\alpha^2+\beta) \\
	\mathbf W_i^{(m)}&=\mathbf W_i^{(c)}=\frac{1}{2( n_x+\lambda)} \quad i=1, \dots, 2n_x, 
\end{align}
where the superscripts $m$ and $c$ denote mean and covariance and $\beta$ incorporates prior knowledge of the distribution of the states, $\mathbf{x}$. Since the observation equation is linear (equation~\ref{ObservationEquation}), the standard Kalman Filter update equations are used to correct the predicted states. The state estimates from forward filtering are used to form a new set of sigma points for the smoother, as described above. The cross-covariance matrix of the states, $\mathbf M$, is also required for computing the smoother gain, as described in the summary of the steps in the URTSS algorithm is given in Table~\ref{tab:UKFAlgorithm}.

@@

	$\sigma_{\nu}^2$ & variance of Fourier transformed Gaussian basis function & \parham{cycles/mm$^2$}\\

>>>>

% \newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}}
\newcommand{\dean}[1]{\textcolor{red}{#1}}
\newcommand{\parham}[1]{\textcolor{blue}{#1}}

@@

In practice, it is difficult to estimate the bandwidth of the cortex using traditional electrophysiological measurements, possibly preventing placement of sensors in accordance to equation~\ref{eq:MinimumSensorDistance}. However, we envisage it may be possible to estimate the spatial bandwidth using other modalities with higher spatial resolution such as fMRI, NIRS or other optical imaging techniques (\cite{Issa2000}). \dean{Reviewer 2, comment 6: From the work of~\citet{Freeman2000}, the expected bandwidth of the human neocortex is approximately 0.4 cycles/mm which requires a maximal sensor spacing of approximately 1.25 mm to avoid distortions due to aliasing.}

Spectral aliasing can be avoided by a proper choice of the spatial sampling distance given the sensors' spectral characteristics. The spatial extent of the sensors results in a spectral low-pass action, thus providing spatial anti-aliasing filtering. Such sensors limit the spatial bandwidth of the observation to a value denoted by $\boldsymbol{\nu}_{cy}$. Aliasing can then be avoided by positioning the sensors according to equation~\ref{eq:MinimumSensorDistance}, replacing $\boldsymbol{\nu}_c$ with $\boldsymbol{\nu}_{cy}$.

@@

The sigma vectors are propagated through the system equations and weighted to form the predicted mean and covariance. The weights are calculated by 
\begin{align}
	\mathbf W_0^{(m)}&=\frac{\lambda}{ n_x+\lambda} \\
	\mathbf W_0^{(c)}&=\frac{\lambda}{ n_x+\lambda}+(1-\alpha^2+\beta) \\
	\mathbf W_i^{(m)}&=\mathbf W_i^{(c)}=\frac{1}{2( n_x+\lambda)} \quad i=1, \dots, 2n_x, 
\end{align}
where the superscripts $m$ and $c$ denote mean and covariance and $\beta$ incorporates prior knowledge of the distribution of the states, $\mathbf{x}$ \dean{(for Gaussian disturbance $\beta$ should be set to 2)}. Since the observation equation is linear (equation~\ref{ObservationEquation}), the standard Kalman Filter update equations are used to correct the predicted states. The state estimates from forward filtering are used to form a new set of sigma points for the smoother, as described above. The cross-covariance matrix of the states, $\mathbf M$, is also required for computing the smoother gain, as described in the summary of the steps in the URTSS algorithm is given in Table~\ref{tab:UKFAlgorithm}.

@@

	$\sigma_{\nu}^2$ & variance of Fourier transformed Gaussian basis function & \parham{(cycles/mm)$^2$}\\
